---
title: "Prelim Analysis"
output: github_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)

library(tidyverse)
library(lubridate)
library(data.table)
# library(RJSONIO)
library(tidygeocoder)
library(ggthemes)
```

```{r}
# import data
```


311 Reports:

- Resident calls and reports violation related to a specific property
- Triggers creation of 311 report
- Inspection is done (as needed)
- If no violation, case closed
- If yes violation, 1 row per violation

How many service requests?

```{r}
# num service requests
df_311 %>% 
  # 1 = prop issue, 0 = other, NA = don't know
  mutate(prop_issues = if_else(location_type == "RESIDENTIAL BUILDING", 1, 0)) %>%   
  # select on nbhd prop issue == 1
  filter(prop_issues == 1) %>% 
  # Cases resulting in prop violation
  # count(status)
  # closed vs violations
  # mutate(violations = if_else(, 1, 0))
  identity()
  

df_311 %>% count(resolution_description)
```



## Maps

What is the ratio of the number of 311 reports resulting in property violations to the total number of 311 reports, by neighborhood?

```{r}
# merge df_311 and df_hpd on bbl

df_311_hpd <- 
  df_311 %>%
  filter(agency == "HPD") %>%
  mutate(bbl = as.numeric(bbl)) %>%
  drop_na(agency, bbl) %>%
  select(1:33) %>%
  select(!c(agency, agency_name))

df_hpd <- 
  df_hpd_viol %>%
  mutate(bbl = as.numeric(bbl)) %>%
  drop_na(bbl)

nyc_property <- left_join(df_311_hpd, df_hpd)

nyc_property %>% count(censustract)
```

## Exploratory Graphs

Top 311 requests by percent of total 

```{r}
df_311 %>% 
  mutate(complaint_type = if_else(str_detect(complaint_type, "Noise"), 
                                  "Noise", complaint_type)) %>%
  group_by(complaint_type) %>% 
  tally() %>%
  arrange(desc(n)) %>%
  rename(complaint_count = n) %>%
  mutate(total_complaints = sum(complaint_count),
         complaint_prop = round((complaint_count/total_complaints)*100, 2)) %>%
  slice(1:10) %>%
  ungroup() %>%
  #mutate(complaint_type = factor(complaint_type, levels = complaint_count)) %>%
  ggplot() +
  geom_col(aes(x = reorder(complaint_type, complaint_count), 
               y = complaint_count),
           fill = "dodgerblue", color = "black") + 
  labs(x = "Request type", y = "Request Count") +
  #scale_fill_brewer(palette = "Spectral") +
  coord_flip() + 
  theme_clean() +
  theme(legend.position = "none")

# and make a table
```

Top 311 agency responders by percent of all requests

```{r}
df_311 %>% 
  group_by(agency) %>% 
  tally() %>%
  arrange(desc(n)) %>%
  rename(agency_count = n) %>%
  mutate(total_agency = sum(agency_count),
         agency_prop = round((agency_count/total_agency)*100, 2)) %>%
  slice(1:10) %>%
  ungroup() %>%
  #mutate(complaint_type = factor(complaint_type, levels = complaint_count)) %>%
  ggplot() +
  geom_col(aes(x = reorder(agency, agency_count), 
               y = agency_count),
           fill = "dodgerblue", color = "black") + 
  labs(x = "Agency type", y = "Request count") +
  theme_clean() +
  theme(legend.position = "none")
```

Longest 311 response time by issue type

```{r}

# Need a bit older data / larger pull

df_311 %>%
  mutate(created_date = lubridate::ymd_hms(created_date),
         closed_date = lubridate::ymd_hms(closed_date),
         resolution_interval = as.double(difftime(closed_date, created_date, units = "days"))) %>% 
  mutate(complaint_type = if_else(str_detect(complaint_type, "Noise"), 
                                "Noise", complaint_type)) %>%
  group_by(complaint_type) %>%
  summarize(avg_resolution_interval = mean(resolution_interval)) %>%
  arrange(desc(avg_resolution_interval)) %>%
  slice(1:10)
```

311 response types (resolutions) -- includes fixed, did not observe, violation

```{r}
# recode responses
df_311 %>%
  mutate(res_desc_category = case_when(
    # Did not observe
    str_detect(resolution_description, "observed no") ~ "did not observe",
    # Fixed
    str_detect(resolution_description, "action to fix") ~ "fixed",
    str_detect(resolution_description, "made an arrest") ~ "fixed",
    # No Action Taken
    str_detect(resolution_description, "no evidence of") ~ "no action taken",
    str_detect(resolution_description, "action was not necessary") ~ "no action taken",
    str_detect(resolution_description, "condition were gone") ~ "no action taken",
    str_detect(resolution_description, "unable to gain entry") ~ "no action taken",
    str_detect(resolution_description, "could not find the individual") ~ "no action taken",
    # Ambiguous
    str_detect(resolution_description, "available later") ~ "ambiguous",
    str_detect(resolution_description, "provided additional information below") ~ "ambiguous",
    str_detect(resolution_description, "reopening") ~ "ambiguous",
    # Duplicate
    str_detect(resolution_description, "duplicate") ~ "duplicate",
    # Ongoing
    str_detect(resolution_description, "report was prepared") ~ "ongoing",
    str_detect(resolution_description, "still open") ~ "ongoing",
    str_detect(resolution_description, "link below") ~ "ongoing",
    # Violations Issued
    str_detect(resolution_description, "violation") ~ "violation",
    # Wrong Agency
    str_detect(resolution_description, "does not fall under") ~ "wrong agency"
    )) %>%
  group_by(agency) %>%
  count(res_desc_category)


df_311 %>%
  pull(resolution_description) %>%
  unique()
```

311 responses by agency

```{r}
# plot the above
```


311 contact type by year

```{r}
df_311 %>%
  mutate(month = month(lubridate::ymd_hms(created_date)),
         year = year(lubridate::ymd_hms(created_date))) %>%
  group_by(open_data_channel_type, year, month) %>%
  count()

# plot, x = date, y = number requests
```

